The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities

### 2021-10-15 text/manuscript_june_2021.Rmd
changed title

---
title: "Recruiting Chapter"
author: 
  - Ozan Jaquette
  - Crystal Han
  - Irma Castañeda
bibliography: ./../other/burd_recruiting_chapter.bib
output: 
  bookdown::pdf_document2:
    toc: FALSE
csl: ./../other/apa.csl
urlcolor: blue
header-includes:
      - \usepackage{pdflscape}
      - \usepackage{geometry}
      - \usepackage{floatrow}
      - \usepackage{setspace}
      #- \doublespacing
      - \floatsetup{capposition=top}
fontsize: 11pt
---

>>>>

---
title: "The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities"
author: 
  - Ozan Jaquette
  - Crystal Han
  - Irma Castañeda
bibliography: ./../other/burd_recruiting_chapter.bib
output: 
  bookdown::pdf_document2:
    toc: FALSE
csl: ./../other/apa.csl
urlcolor: blue
header-includes:
      - \usepackage{pdflscape}
      - \usepackage{geometry}
      - \usepackage{floatrow}
      - \usepackage{setspace}
      #- \doublespacing
      - \floatsetup{capposition=top}
fontsize: 11pt
---
